Data 621---HW1---Regression Model---Version 2

### 2020-09-08 HW1/RegModel_Adler.Rmd
Center & Scale not enough. Moving to `caret` package

### Transformations
The first transform applied will be centering and scaling, as discussed above.

```{r centerScale}
MBmelt[, Value := scale(Value, center = TRUE, scale = TRUE), keyby = Metric]
```

At this point we would hope to see Gaussian-looking densities.
```{r plotScaled}
ggplot(MBmelt, aes(x = Value)) + geom_density() +
  facet_wrap(~ Metric, scales = 'free')
```

@@

>>>>

### Transformations
#### Centering and Scaling
The first transform applied will be centering and scaling, as discussed above.
We will store the means and standard deviations so that we can transform the
predictions back to their respective distributions.

```{r centerScale}
MBmeltSC <- copy(MBmelt)
MBmeltUnscale <- MBmeltSC[, .(Mean = mean(Value), SD = sd(Value)),
                          keyby = Metric]
MBmeltSC[, Value := scale(Value, center = TRUE, scale = TRUE), keyby = Metric]
knitr::kable(MBmeltUnscale, digits = 2L, caption = 'Data Means and SDs')
```

At this point we would hope to see Gaussian-looking densities.
```{r plotScaled}
ggplot(MBmeltSC, aes(x = Value)) + geom_density() +
  facet_wrap(~ Metric, scales = 'free')
```

@@

All of this indicates that there will need to be further processing.

#### Box-Cox transformations
One of classic data transformations to induce normality is the Box-Cox
transform. It is defined as:
\[
y(\lambda) =
\begin{cases}
\frac{y^\lambda - 1}{\lambda}, &\quad \lambda \neq 0\\
\ln{y}, &\quad \lambda = 0
\end{cases}
\]

Unfortunately, this is only defined on positive data. Therefore, the unscaled
data will need to be used. While in theory it would be nice to transform each
column as best possible, that makes for very difficult reconstruction. At this
point, we will pivot to continuing the analysis using the `caret` package which
takes care of a lot of the computational issues.
